---
title: "Introduction to StatComp20002 and two functions"
author: "Hongrui Cai"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20002 and two functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20002__ is a simple R package developed to implement two different R functions and all functions in the homeworks of the owner 20002 during the course "Statistical Computing". Two functions are considered, namely, _SampleChain_ (generate Metropolis chain from giving multinomial distribution) and _rcauchyMH_ (generate random samples from Cauchy distribution by MH sampler). For each function, R version is produced.

## Implementation of _SampleChain_ and _rcauchyMH_

The source R code for _SampleChain_ is as follows.
```{r,eval=FALSE}
function(N, start){
  # generates a Metropolis chain for multinomial distribution
  # with random walk proposal distribution and starting value start
  sizes <- c(125,18,20,34)
  x <- rep(0, N)
  x[1] <- start
  u <- runif(N)
  v <- runif(N,-0.25,0.25)
  prob <- function(theta){
    p <- c(0.5+theta/4,(1-theta)/4,(1-theta)/4,theta/4)
  }# the probabilities of the corresponding multinomial distribution
  prob.ratio <- function(x1,x2){
    prod(prob(x1)^sizes/prob(x2)^sizes)
  }
  
  for (i in 2:N){
    xt <- x[i-1]
    y <- xt + v[i] # candidate point
    r <- min(prob.ratio(y,xt),1)
    if (!is.nan(r) && u[i] <= r){
      x[i] <- y
    }else{
      x[i] <- xt
    }
  }
  return(x)
}
```

The source R code for _rcauchyMH_ is as follows.
```{r, eval=FALSE}
function(n,theta=0,eta=1){
  x <- numeric(n)
  u <- runif(n)
  x[1] <- rnorm(1)
  k <- 0
  # cauchy functions
  f <- function(x, theta=1, eta=0){
    out <- 1/(pi * theta * (1+((x-eta)/theta)^2))
    return(out)
  }
  
  for(i in 2:n){
    xt <- x[i-1]
    y <- rnorm(1,mean=xt)
    R <- f(y)*dnorm(xt,mean=y)/(f(xt)*dnorm(y,mean=xt))
    if(u[i] <= R){
      x[i] <- y
    }else{
      x[i] <- xt
      k <- k+1
    }
  }
  return(x)
}
```

## Examples of _SampleChain_ and _rcauchyMH_

The R code for _SampleChain_ and _rcauchyMH_ is as follows.
```{r,eval=TRUE}
library(StatComp20002)
example_Metropolis = SampleChain(N=10, start=1)
example_Cauchy = rcauchyMH(n=10, theta=0, eta=1)
print(example_Metropolis)
print(example_Cauchy)
plot(example_Metropolis,type='l')
```
